Open archaeology, open source?

### 2024-02-02 analysis/_03-data_methodology.qmd
Remove obsolete TODO

# Extract clean repos from GitHub URLs
oarch |>
  mutate(
    gh_repo = str_match(oarch$github, "^https://github.com/([\\w-\\.]+/[\\w-\\.]+)/?.*?$")[,2]
  ) ->
  oarch

# TODO: exclude peripheral repos that throw things off
# * Big boys like QField (see _06-network.qmd)
# * ArchaeoLines – ends up picking up the whole stellarium repo, which is huge
# * aDNA??
```

>>>>

# Extract clean repos from GitHub URLs
oarch |>
  mutate(
    gh_repo = str_match(oarch$github, "^https://github.com/([\\w-\\.]+/[\\w-\\.]+)/?.*?$")[,2]
  ) ->
  oarch
```
